% File: ~/domain/domain/loadBalancer/LoadBalancer.tex 
% What: "@(#) LoadBalancer.tex, revA"

\noindent {\bf Files}   \\
\indent \#include $<\tilde{ }$/domain/loadBalancer/LoadBalancer.h$>$  \\

\noindent {\bf Class Declaration}  \\
\indent class LoadBalancer \\

\noindent {\bf Class Hierarchy} \\
\indent {\bf LoadBalancer} \\


\noindent {\bf Description}  \\
\indent A LoadBalancer is an object used to balance a
PartitionedDomain. The LoadBalancer does this by invoking methods in
the DomainPartitioner object with which it is associated. \\

\noindent {\bf Class Interface}  \\
\indent\indent  // Constructor  \\
\indent\indent {\em LoadBalancer(); }\\ \\
\indent\indent // Destructor  \\
\indent\indent {\em virtual~ $\tilde{}$LoadBalancer();}  \\ \\
\indent\indent // Public Methods  \\
\indent\indent {\em virtual void setLinks(DomainPartitioner
\&thePartitioner);} \\ 
\indent\indent {\em virtual int balance(Graph \&theWeightedGraph) =0;} \\ \\
\indent\indent // Public Methods  \\
\indent\indent {\em DomainPartitioner *getDomainPartitioner(void); }\\


\noindent {\bf  Constructor  }\\
\indent {\em LoadBalancer(); }\\ 
Sets the pointer to the associated PartitionedDomain to be $0$. \\

\noindent {\bf Destructor } \\
\indent {\em virtual~ $\tilde{}$LoadBalancer();}  \\ 
Does nothing. Provided so the subclasses destructor will be called. \\

\noindent {\bf  Public Methods} \\
\indent {\em virtual void setLinks(DomainPartitioner
\&thePartitioner);} \\
Sets the pointer to the DomainPartitioner object associated with the
LoadBalancer to point to {\em thePartitioner}. \\

{\em virtual int balance(Graph \&theWeightedGraph) =0;} \\ 
Each subclass must provide an implementation of this method. This
method is invoked to balance the PartitionedDomain. The Graph {\em
theWeightedGraph} is a weighted graph in which the vertices represent
the Subdomains, the edges Subdomains sharing common boundary nodes and
the weight the cost of the previous Subdomain calculations (determined
by invoking {\em getCost()} on the Subdomains). \\


\noindent {\bf Protected Methods}  \\
\indent {\em DomainPartitioner *getDomainPartitioner(void); }\\
Returns a pointer to the DomainPartitioner. If no DomainPartitioner
has been set, a warning message is printed and $0$ returned. \\




