% File: ~/domain/domain/loadBalancer/SwapHeavierToLighterNeighbours.tex 
% What: "@(#) SwapHeavierToLighterNeighbours.tex, revA"

\noindent {\bf Files}   \\
\indent \#include $<\tilde{ }$/domain/loadBalancer/SwapHeavierToLighterNeighbours.h$>$  \\

\noindent {\bf Class Declaration}  \\
\indent class SwapHeavierToLighterNeighbours: public LoadBalancer \\

\noindent {\bf Class Hierarchy} \\
\indent  LoadBalancer \\
\indent\indent {\bf SwapHeavierToLighterNeighbours} \\


\noindent {\bf Description}  \\
\indent A SwapHeavierToLighterNeighbours is an object used to balance a
PartitionedDomain. It does this by shedding the boundary vertices on
the heaviest loaded partition (subdomain). \\

\noindent {\bf Class Interface}  \\
\indent\indent  // Constructors  \\
\indent\indent {\em SwapHeavierToLighterNeighbours(); }\\ 
\indent\indent {\em SwapHeavierToLighterNeighbours(double
factorGreater, int numReleases);} \\ \\
\indent\indent // Destructor  \\
\indent\indent {\em virtual~ $\tilde{}$SwapHeavierToLighterNeighbours();}  \\ \\
\indent\indent // Public Methods  \\
\indent\indent {\em virtual int balance(Graph \&theWeightedGraph) =0;} \\ \\


\noindent {\bf  Constructors  }\\
\indent {\em SwapHeavierToLighterNeighbours(); }\\ 
Sets {\em numRealeases} to $1$ and {\em factorGreater} to $1.0$. These
are the paramemeters used in the {\em balance()} method. \\

\indent {\em SwapHeavierToLighterNeighbours(double factorGreater, int
numReleases);}\\ 
Sets the parameters used in the {\em balance()} method. \\

\noindent {\bf Destructor } \\
\indent {\em virtual~ $\tilde{}$SwapHeavierToLighterNeighbours();}  \\ 
Does nothing. \\

\noindent {\bf  Public Methods} \\
\indent {\em virtual int balance(Graph \&theWeightedGraph) =0;} \\ 
For {\em numRelease} times the Vertices of {\em theWeightedGraph} are
iterated through. For each Vertex, $i$, the weight of the Vertex is compared
to those of it's adjacent Vertices, $other$, (this is done by looping through
the adjacency ID of the Vertex), if the vertex weight is {\em
factorGreater} times greater than the other Vertices load then {\em
swapBoundary(i, other)} is invoked on the DomainPartitioner. Returns
$0$ if successful, otherwise a negative number and a warning message
are returned if either no link has been set to the DomainPartitioner
or {\em swapBoundary()} returns a negative number. \\



