%File: ~/OOP/domain/pattern/PathSeries.tex
%What: "@(#) PathSeries.tex, revA"

\noindent {\bf Files}   \\
\indent \#include $<\tilde{ }$domain/pattern/PathSeries.h$>$  \\

\noindent {\bf Class Declaration}  \\
\indent class PathSeries: public DomainComponent  \\

\noindent {\bf Class Hierarchy} \\
\indent MovableObject \\
\indent\indent TimeSeries \\
\indent\indent\indent {\bf PathSeries} \\

\noindent {\bf Description} \\ 
\indent The PathSeries class is a concrete subclass of TimeSeries.
The relationship between the pseudo time and the load factor follows
a user specified path. The path points are specified at constant time
intervals. For a pseudo time not at a path point, linear interpolation
is performed to determine the load factor. If the time specified is
beyond the last path point a load factor of $0.0$ will be returned.\\

\noindent {\bf Class Interface} \\
\indent // Constructors \\ 
\indent {\em PathSeries(Vector \&thePath, double dT; double cFactor);}\\ 
\indent {\em PathSeries(char *fileName, double dT; double cFactor);}\\ 
\indent {\em PathSeries();}\\ \\
\indent // Destructor \\ 
\indent {\em virtual $\tilde{ }$PathSeries();}\\  \\
\indent // Public Methods \\ 
\indent {\em  virtual double getFactor(double pseudoTime);}\\
\indent {\em  virtual int sendSelf(int commitTag, Channel \&theChannel);}\\
\indent {\em  virtual int recvSelf(int commitTag, Channel \&theChannel,
FEM\_ObjectBroker \&theBroker);}\\
\indent {\em  virtual void Print(ostream \&s, int flag =0);}\\

\noindent {\bf Constructor} \\ 
\indent {\em PathSeries(Vector \&thePath, double dT; double cFactor);}\\ 
Used to construct a PathSeries when the data points are specified in a
Vector. The tag TSERIES\_TAG\_PathSeries is passed to the TimeSeries
The tag TSERIES\_TAG\_PathSeries is passed to the TimeSeries
constructor. Sets the constant factor used in the relation to {\em
cFactor}. Constructs a new Vector equal to {\em thePath} containing the
data points which are specified at {\em dT} time intervals. Prints a
warning message if no space is available for the Vector.\\

\indent {\em PathSeries(char *fileName, double dT; double cFactor);}\\ 
Used to construct a PathSeries when the data points are specified in a
file. The tag TSERIES\_TAG\_PathSeries is passed to the TimeSeries
constructor. Sets the constant factor used in the relation to {\em
cFactor}. Opens the file containing and reads in the data points into
a new Vector which are specified at {\em dT} time intervals. Prints a
warning message if no space is available for the Vector or if the file
could not be found.\\


\indent {\em PathSeries();}\\ 
For a FEM\_ObjectBroker to instantiate an empty PathSeries, recvSelf()
must be invoked on this object. The tag TSERIES\_TAG\_PathSeries is
passed to the TimeSeries constructor. \\


\noindent {\bf Destructor} \\
\indent {\em virtual $\tilde{ }$PathSeries();}\\ 
Invokes the destructor on the Vector created to hold the data
points. \\


\noindent {\bf Public Methods} \\
\indent {\em  virtual double getFactor(double pseudoTime);}\\
Determines the load factor based on the {\em pseudoTime} and the data
points. Returns $0.0$ if {\em pseudoTime} is greater than time of last
data point, otherwise returns a linear interpolation of the data
points times the factor {\em cFactor}. \\

\indent {\em  virtual int sendSelf(int commitTag, Channel
\&theChannel);}\\
Creates a vector of size 4 into which it places {\em cFactor}, {\em
dT}, the size of {\em thePath} and another database tag for {\em
thaPath} Vector.  Invokes {\em sendVector()} on the Channel with this
newly created Vector object, and the {\em sendVEctor()} on {\em
thePath}. \\

\indent {\em  virtual int recvSelf(int commitTag, Channel \&theChannel,
FEM\_ObjectBroker \&theBroker);}\\
Does the mirror image of {\em sendSelf()}. \\

\indent {\em  virtual void Print(ostream \&s, int flag =0) =0;}\\
Prints the string 'PathSeries', the factor{\em cFactor}, and the time
increment {\em dT}. If {\em flag} is equal to $1.0$ the load path
Vector is also printed.


