%File: ~/OOP/domain/pattern/PathTimeSeries.tex
%What: "@(#) PathTimeSeries.tex, revA"

\noindent {\bf Files}   \\
\indent \#include $<\tilde{ }$domain/pattern/PathTimeSeries.h$>$  \\

\noindent {\bf Class Declaration}  \\
\indent class PathTimeSeries: public DomainComponent  \\

\noindent {\bf Class Hierarchy} \\
\indent MovableObject \\
\indent\indent TimeSeries \\
\indent\indent\indent {\bf PathTimeSeries} \\

\noindent {\bf Description} \\ 
\indent The PathTimeSeries class is a concrete subclass of TimeSeries.
The relationship between the pseudo time and the load factor follows
a user specified path. The path points are specified at user specified
time values. For a pseudo time not at a path point, linear interpolation
is performed to determine the load factor. If the time specified is
beyond the last path point a load factor of $0.0$ will be returned.\\

\noindent {\bf Class Interface} \\
\indent // Constructors \\ 
\indent {\em PathTimeSeries(Vector \&thePath, Vector \&time; double cFactor);}\\ 
\indent {\em PathTimeSeries(char *fileName, Vector \&time; double cFactor);}\\ 
\indent {\em PathTimeSeries();}\\ \\
\indent // Destructor \\ 
\indent {\em virtual $\tilde{ }$PathTimeSeries();}\\  \\
\indent // Public Methods \\ 
\indent {\em  virtual double getFactor(double pseudoTime);}\\
\indent {\em  virtual int sendSelf(int commitTag, Channel \&theChannel);}\\
\indent {\em  virtual int recvSelf(int commitTag, Channel \&theChannel,
FEM\_ObjectBroker \&theBroker);}\\
\indent {\em  virtual void Print(ostream \&s, int flag =0);}\\

\noindent {\bf Constructor} \\ 
\indent {\em PathTimeSeries(Vector \&thePath, Vector \&time; 
double cFactor);}\\ 
Used to construct a PathTimeSeries when the data points and time
values are specified in a Vectors. The tag
TSERIES\_TAG\_PathTimeSeries is passed to the TimeSeries 
constructor. Sets the constant factor used in the relation to {\em
cFactor}. Constructs two new Vectors equal to {\em thePath} and {\em
time}. Prints a warning message if no space is available for the
Vectors or if the two Vectors are not of the same size.\\ 

\indent {\em PathTimeSeries(char *filePath, file *timeName; double
cFactor);}\\  
Used to construct a PathTimeSeries when the data points and time
values are specified in files. The tag TSERIES\_TAG\_PathTimeSeries is
passed to the TimeSeries constructor. Sets the constant factor used in
the relation to {\em cFactor}. Opens the two files and counts the
number of entries in each, if different prints a warning message and
returns. Constructs the two vectors for the data and reads the data
from the files into the two vectors. Prints a warning message if no
space is available for the Vectors.\\

\indent {\em PathTimeSeries();}\\ \\
For a FEM\_ObjectBroker to instantiate an empty PathTimeSeries, recvSelf()
must be invoked on this object. The tag TSERIES\_TAG\_PathTimeSeries is
passed to the TimeSeries constructor. \\


\noindent {\bf Destructor} \\
\indent {\em virtual $\tilde{ }$PathTimeSeries();}\\ 
Invokes the destructor on the two Vectors created to hold the data. \\

\noindent {\bf Public Methods} \\
\indent {\em  virtual double getFactor(double pseudoTime);}\\
Determines the load factor based on the {\em pseudoTime} and the data
points. Returns $0.0$ if {\em pseudoTime} is greater than time of last
data point, otherwise returns a linear interpolation of the data
points times the factor {\em cFactor}. \\

\indent {\em  virtual int sendSelf(int commitTag, Channel
\&theChannel);}\\
Creates a vector of size 4 into which it places {\em cFactor}, the
size of {\em thePath} and two  database tag for {\em 
thaPath} and {\em time} Vectors.  Invokes {\em sendVector()} on the
Channel with this newly created Vector object, and then again with the
{\em time} and {\em thePath} Vectors.\\

\indent {\em  virtual int recvSelf(int commitTag, Channel \&theChannel,
FEM\_ObjectBroker \&theBroker);}\\
Does the mirror image of {\em sendSelf()}. \\

\indent {\em  virtual void Print(ostream \&s, int flag =0) =0;}\\
Prints the string 'PathTimeSeries', the factor{\em cFactor}, and the time
increment {\em dT}. If {\em flag} is equal to $1.0$ {\em
thePath} and {\em time} Vector are also printed\\