%File: ~/handler/ErrorHandler.tex
%What: "@(#) ErrorHandler.tex, revA"

\noindent {\bf Files}   \\
\indent \#include $<\tilde{ }$/handler/ErrorHandler.h$>$  \\

\noindent {\bf Class Declaration}  \\
\indent class ErrorHandler \\

\noindent {\bf Class Hierarchy} \\
\indent {\bf ErrorHandler} \\

\noindent {\bf Description}  \\
\indent The ErrorHandler class is an abstract class which is
introduced to allow error information to be processed during the
execution of the program. The interface defines two pure virtual
methods {\em warning()} and {\em fatal()}. {\em warning()} is a method
which is called by an object when an error has occured but the program
can continue running after the error has been logged; {\em fatal()} is
invoked when the error is so serious that the program must be
terminated. \\ 

QUESTION: SHOULD THE DOMAIN/RECORDER CLASSES HAVE A shutdown() METHOD? \\

\noindent {\bf Class Interface} \\
\indent // Constructor \\
\indent {\em ErrorHandler();}\\ \\
\indent // Destructor \\
\indent {\em virtual $\tilde{ }$ErrorHandler();}\\ \\
\indent // Public Methods  \\
\indent {\em virtual void warning(const char *msg, ...) =0;}\\
\indent {\em virtual void fatal(const char *msg, ...) =0;}\\ \\
\indent // Protected Methods  \\
\indent {\em void outputMessage(ostream \&theStream, const char *msg, va\_list args);} \\

\noindent {\bf Constructor}  \\
\indent {\em ErrorHandler();}  \\ 
Does nothing.\\

\noindent {\bf Destructor} \\
\indent {\em virtual~ $\tilde{}$ErrorHandler();}\\ 
Does nothing. \\

\noindent {\bf Public Methods }  \\
\indent {\em virtual void warning(const char *msg, ...) =0;}\\
Invoked by an object when an error has occurred. The program will
continue running after this method has been invoked. The first
argument is a pointer to a format string that specifies how
subsequent (or arguments accessed via the variable-length ellipses
argument are converted for output. As for {\em printf()}, the format
string is composed of ordinary characters (not \%) which are copied to
the log unmodified and conversion specifications, which fetches the
next argument from the ellipses. Conversion specification is
introduced by the \% character and followed by one of the following
flags {\bf d}, {\bf f} and {\bf s}, for integers, doubles and strings
respectively. \\


\indent {\em virtual void playback(const char *msg, ...) =0;}\\ 
Invoked by an object when an error has occurred. The program will be
terminated by this method. The arguments are the same as for the {\em
record()} method.\\ 

\noindent {\bf Protected Methods }  \\
\indent {\em void outputMessage(ostream \&theStream, const char *msg,
va\_list args);}\\ 
Will print to the ostream {\em theStream} the error message, where
{\em msg} is the format string  and {\em va\_list} is the list created
from the varying number of arguments passed to the {\em warning()} or
{\em fatal()} methods. It is up to the calling object to both create
{\em va\_start()} and destroy {\em va\_end()} this list. 

