%File: ~/OOP/system_of_eqn/linearSOE/bandSPD/ProfileSPDLinDirectSkypackSolver.tex
%What: "@(#) ProfileSPDLinDirectSkypackSolver.tex, revA"

\noindent {\bf Files}   \\
\indent \#include $<\tilde{ }$/system\_of\_eqn/linearSOE/profileSPD/ProfileSPDLinDirectSkypackSolver.h$>$  \\

\noindent {\bf Class Declaration}  \\
\indent class ProfileSPDLinDirectSkypackSolver: public LinearSOESolver  \\

\noindent {\bf Class Hierarchy} \\
\indent MovableObject \\
\indent\indent  Solver \\
\indent\indent\indent LinearSOESolver \\
\indent\indent\indent\indent ProfileSPDLinSolver \\
\indent\indent\indent\indent\indent {\bf ProfileSPDLinDirectSkypackSolver} \\

\noindent {\bf Description}  \\
\indent A ProfileSPDLinDirectSkypackSolver object can be constructed
to solve a ProfileSPDLinSOE object. It does this by direct means using
the routines supplied in the SKYPACK library, a library which uses the
BLAS levels 1,2 and 3 for the factorization and substitution. 

The routines in SKYPACK require a number of work areas: {\em int
block[3]} and {\em double invD[size]}. In addition, to allow the use
of the BLAS 2 and 3, work areas {\em double rw[mRows x mCols]}, {\em
double tw[mRows x mRows]} and {\em int index[max(mCols,mRows)]} are 
created. \\


\noindent {\bf Interface}  \\
\indent\indent Constructors \\
\indent\indent {\em ProfileSPDLinDirectSkypackSolver();}  \\ 
\indent\indent {\em ProfileSPDLinDirectSkypackSolver(int mCols, mRows);}  \\ \\
\indent\indent Destructor \\
\indent\indent {\em  $\tilde{}$ProfileSPDLinDirectSkypackSolver();}\\  \\
\indent\indent Public Methods \\
\indent\indent {\em int solve(void);} \\
\indent\indent {\em  int setSize(void);} \\
\indent\indent {\em int sendSelf(int commitTag, Channel \&theChannel);}\\ 
\indent\indent {\em int recvSelf(int commitTag, Channel \&theChannel,
FEM\_ObjectBroker \&theBroker);}\\ 


\noindent {\bf Constructors}  \\
\indent {\em ProfileSPDLinDirectSkypackSolver();}  \\
A unique class tag (defined in $<$classTags.h$>$) is passed to the
ProfileSPDLinSolver constructor. Sets {\em mCols} and {\em mRows}
equal to $0$ and does not try and allocate any memory for the work arrays.\\

\indent {\em ProfileSPDLinDirectSkypackSolver(int mCols, int mRows);}  \\
A unique class tag (defined in $<$classTags.h$>$) is passed to the
ProfileSPDLinSolver constructor. Sets {\em mCols} and {\em mRows} and
allocates space in memory for the work arrays {\em rw}, {\em tw} and
{\em index}. If not enough memory is available in memory, {\em mCols}
and {\em mRows} is set equal to $0$ and an error message is printed. \\

\noindent {\bf Destructor} \\
\indent {\em $\tilde{}$ProfileSPDLinDirectSkypackSolver();}\\ 
Invokes delete on any work areas that have been constructed. \\

\noindent {\bf Public Member Functions }  \\
\indent {\em  int solve(void);} \\
The solver first copies the B vector into X and then solves the
BandSPDLinSOE system. If the matrix has not been factored, the matrix
is first factored using the SKYPACK routine {\em skysf2()}, if {\em
mCols} and {\em mRows} equal $0$, or {\em skypf2()}. {\em skysf2()} is
a routine which uses the BLAS level 1 routines, {\em skypf2()} is a
routine which uses BLAS levels 2 and 3. If {\em skypf2()}
has been called, {\em invD} is set up. Once the matrix has been
factored, {\em skyss()} is called. If the solution is successfully
obtained, i.e. the {\em skyss()} routine returns $0$ in the INFO
argument, $0$ is returned, otherwise it prints a warning message and
returns INFO. The solve process changes $A$ and $X$. \\   

\indent {\em  int setSize(void);} \\
Is responsible for setting the {\em block} information required by the
SKYPACK routines (block[0]=1; block[1]=size, block[2]=1) and for
creating space for the {\em invD} work array. Returns $0$ if
successful, otherwise a warning message is printed and a $-1$ is
returned. \\

\indent {\em  int sendSelf(int commitTag, Channel \&theChannel);} \\ 
Does nothing but return $0$. \\

\indent {\em  int recvSelf(int commitTag, Channel \&theChannel, FEM\_ObjectBroker
\&theBroker);} \\ 
Does nothing but return $0$. \\







