%File: ~/recorder/MaxNodeDispRecorder.tex
%What: "@(#) MaxNodeDispRecorder.tex, revA"

\noindent {\bf Files}   \\
\indent \#include $<\tilde{ }$/recorder/MaxNodeDispRecorder.h$>$  \\

\noindent {\bf Class Declaration}  \\
\indent class MaxNodeDispRecorder: public Recorder\\

\noindent {\bf Class Hierarchy} \\
\indent Recorder \\
\indent\indent {\bf MaxNodeDispRecorder} \\

\noindent {\bf Description}  \\
\indent The MaxNodeDispRecorder class is used to store information
about the absolute maximum nodal displacement at a number of specified
Nodes for a specified degree of freedom during an analysis. \\

\noindent {\bf Class Interface} \\
\indent // Constructor \\
\indent {\em MaxNodeDispRecorder(int dof, const ID \&nodeTags, Domain
\&theDomain);}\\ \\ 
\indent // Destructor \\
\indent {\em $\tilde{ }$MaxNodeDispRecorder();}\\ \\
\indent // Public Methods  \\
\indent {\em int record(int commitTag);}\\
\indent {\em int playback(int commitTag);}\\
\indent {\em void restart(void);}\\ 

\noindent {\bf Constructor}  \\
\indent {\em MaxNodeDispRecorder(int dof, const ID \&nodeTags,
Domain \&theDomain);}\\ 
Creates a $0$ Vector object of size equal to the size of {\em
nodeTags} to store the maximum nodal displacements
and creates an ID object equal to {\em nodeTags} to store the Node
tags. \\

\noindent {\bf Destructor} \\
\indent {\em virtual~ $\tilde{}$MaxNodeDispRecorder();}\\ 
Does nothing. \\

\noindent {\bf Public Methods }  \\
\indent {\em int record(int commitTag);}\\
For each node in {\em nodeTags} the value of the {\em dof}'th committed
displacement is obtained. If the absolute value of this is greater
than the value currently stored in the Vector of max displacements,
the value in the Vector is updated. If no Node exists in {\em
theDomain} with the tag or the Node does not have a {\em dof}'th
degree-of-freedom associated with it $0$ is entered in the
Vector. Returns $0$. \\

\indent {\em int playback(int commitTag);}\\
Prints to {\em cerr} the Vector containing the maximum absolute nodal
displacements. Note, at the end of the analysis, what is printed is
independent of {\em commitTag}. Returns $0$. \\

\indent {\em void restart(void);}\\ 
Zeros the Vector of maximum nodal displacements.