%File: ~/OOP/analysis/analysis/DomainDecompositionAnalysis.tex
%What: "@(#) DomainDecompositionAnalysis.tex, revA"

UNDER CONSTRUCTION

\noindent {\bf Files}   \\
\indent \#include $<\tilde{
}$/analysis/analysis/DomainDecompositionAnalysis.h$>$  \\ 

\noindent {\bf Class Declaration}  \\
\indent class DomainDecompositionAnalysis: public Analysis, public MovableObject;  \\

\noindent {\bf Class Hierarchy} \\
\indent Analysis \\
\indent MovableObject \\
\indent\indent {\bf DomainDecompositionAnalysis} \\

\noindent {\bf Description} \\ 
\indent DomainDecompositionAnalysis is a subclass of Analysis, 
it is used when performing an analysis using the domain decomposition
method to solve the equations. Its public member functions are all
virtual to allow for the generalization of the 
class. The following are the aggregates of such an analysis type:
\begin{itemize}
\item {\bf AnalysisModel} - a container class holding the FE\_Element
and DOF\_Group objects created by the ConstraintHandler object. 
\item {\bf ConstraintHandler} - a class which creates the DOF\_Group
and FE\_Element objects, the type of objects created depending on how
the specified constraints in the domain are to be handled. 
\item {\bf DOF\_Numberer} - a class responsible for providing equation
numbers to the individual degrees of freedom in each DOF\_Group object.
\item {\bf LinearSOE} - a numeric class responsible for the creation
and subsequent solution of large systems of linear equations of the
form $Ax = b$, where A is a matrix, and x and b are vectors.
\item {\bf IncrementalIntegrator} - an algorithmic class which provides
methods which are invoked by the FE\_Element to determine their
current tangent and residual matrices; that is this is the class that
sets up the system of equations.  It also provides the {\em
update()} method which is invoked to set up the appropriate dof
response values once the solution algorithm has formed and solved the
system of equations.
\item {\bf DomainDecompositionAlgo} - an algorithmic class specifying the
sequence of operations to be performed in determining the response
for the external dof and placing these in the system of equations.
\item {\bf DomainSolver} - an algorithmic class specifying the
sequence of operations to be performed in performing the numerical 
operations.
\end{itemize}


\noindent {\bf Class Interface} \\
\indent {\bf Constructors} \\
\indent {\em DomainDecompositionAnalysis(Subdomain \&theDomain, \\
\indent\indent\indent\indent\indent\indent\indent ConstraintHandler
\&theHandler, \\ 
\indent\indent\indent\indent\indent\indent\indent DOF\_Numberer \&theNumberer, \\
\indent\indent\indent\indent\indent\indent\indent AnalysisModel \&theModel,\\
\indent\indent\indent\indent\indent\indent\indent DomainDecompAlgo \&theSolnAlgo,\\
\indent\indent\indent\indent\indent\indent\indent IncrementalIntegrator \&theIntegrator,\\
\indent\indent\indent\indent\indent\indent\indent LinearSOE \&theSOE, \\
\indent\indent\indent\indent\indent\indent\indent DomainDecompositionSolver \&theSolver);} \\
\indent {\em DomainDecompositionAnalysis(Subdomain \&theDomain);} \\
\indent {\em DomainDecompositionAnalysis(int classTag, Subdomain
\&theDomain);}\\ \\
\indent // Destructor \\
\indent {\em virtual~ $\tilde{}$DomainDecompositionAnalysis();}\\ \\
\indent // Public Methods \\
\indent {\em virtual int analyze(void);} \\
\indent {\em virtual void domainChanged(void);} \\
\indent {\em int getNumExternalEqn(void);} \\
\indent {\em     virtual int  computeInternalResponse(void);}\\
\indent {\em     virtual int  formTangent(void);}\\
\indent {\em     virtual int  formResidual(void);}\\
\indent {\em int  formTangVectProduct(Vector \&u);}\\
\indent {\em virtual Matrix \&getTangent();}\\
\indent {\em virtual Vector \&getResidual();}\\
\indent {\em const Vector \&getTangVectProduct();}\\
\indent {\em int sendSelf(Channel \&theChannel, FEM\_ObjectBroker
\&theBroker);}\\ 
\indent {\em int recvSelf(Channel \&theChannel, FEM\_ObjectBroker
\&theBroker);}\\\\ 
\indent // Protected Member Functions  \\
\indent {\em Subdomain  *getSubdomainPtr(void) const;} \\
\indent {\em ConstraintHandler *getConstraintHandlerPtr(void) const;}\\
\indent {\em DOF\_Numberer *getDOF\_NumbererPtr(void) const;}\\
\indent {\em AnalysisModel  *getAnalysisModelPtr(void) const;}\\
\indent {\em DomainDecompAlgo  *getDomainDecompAlgoPtr(void) const;}\\
\indent {\em IncrementalIntegrator *getIncrementalIntegratorPtr(void) const;}\\
\indent {\em LinearSOE *getLinSOEPtr(void) const;}\\
\indent {\em DomainSolver *getDomainSolverPtr(void) const;} \\


\noindent {\bf Constructors} \\
\indent {\em DomainDecompositionAnalysis(Subdomain \&theDomain, \\
\indent\indent\indent\indent\indent\indent\indent ConstraintHandler
\&theHandler, \\ 
\indent\indent\indent\indent\indent\indent\indent DOF\_Numberer \&theNumberer, \\
\indent\indent\indent\indent\indent\indent\indent AnalysisModel \&theModel,\\
\indent\indent\indent\indent\indent\indent\indent DomainDecompAlgo \&theSolnAlgo,\\
\indent\indent\indent\indent\indent\indent\indent IncrementalIntegrator \&theIntegrator,\\
\indent\indent\indent\indent\indent\indent\indent LinearSOE \&theSOE, \\
\indent\indent\indent\indent\indent\indent\indent DomainDecompositionSolver \&theSolver);} \\
The constructor sets all the links required by the objects in the aggregation. To
do this it invokes {\em setLinks(theDomain)} on {\em theModel},
{\em setLinks(theSubdomain,theModel,theIntegrator)} on {\em theHandler}, 
{\em setLinks(theModel)} on {\em theNumberer}, it invokes {\em
setLinks(theModel, theSOE)} on {\em theIntegrator}, and it invokes {\em
setLinks(theModel,theIntegrator, theSOE,theSolver,theSubdomain)} on {\em
theSolnAlgo}. Finally it invokes {\em setAnalysis(*this)} on {\em theSubdomain}. \\

\indent {\em DomainDecompositionAnalysis(Subdomain \&theDomain);} \\
A constructor that is used when creating a DomainDecompositionObject which
is to receive itself afterwards. Sets the links to the Subdomain. It is
essential that this object {\em recvSelf()} before DomainDecompositionAnalysis
methods are invoked as their invocation will cause segmentation faults. 
Invokes {\em setAnalysis(this)} on the Subdomain. \\

{\em DomainDecompositionAnalysis(int classTag, Subdomain \&theDomain);}\\
Provided for subclasses to use. Invokes {\em setAnalysis(this)} on the
Subdomain. \\ 


\noindent {\bf Destructor} \\
\indent {\em virtual~ $\tilde{}$DomainDecompositionAnalysis();}\\ 

\noindent {\bf Public Methods}\\
\indent {\em virtual int analyze(void);} \\
Causes an error message to be output and returns $-1$. \\

{\em virtual void domainChanged(void);} \\
Method used to inform the object that the domain has changed. The
DomainDecompositionAnalysis object then performs the following: \\ {\em
\indent\indent theAnalysisModel-$>$clearAll(),
theConstraintHandler-$>$clearAll();\\ 
\indent\indent numExtEqn =
theConstraintHandler-$>$handle(theSubdomain-$>$getExternalNodes());\\ 
\indent\indent theDOFnumberer-$>$number(theExternalDOFsDOFGrps);  \\
\indent\indent theLinSysOfEqn-$>$setSize(theAnalysisModel-$>$getDOFGraph);  \\
\indent\indent theIntegrator-$>$domainChanged(); \\
\indent\indent theAlgorithm-$>$domainChanged(); \\ }
Finally {\em tangFormed} is marked as {\em false}. \\

{\em int getNumExternalEqn(void);} \\
A method to return the number of external degrees-of-freedom on the
Subdomain interface, this information is returned when {\em handle()}
is invoked on {\em theConstraintHandler}. \\

{\em     virtual int  computeInternalResponse(void);}\\
A method which invokes {\em solveCurrentStep()} on {\em theAlgorithm}.  \\

{\em     virtual int  formTangent(void);}\\
A method to form the condensed tangent matrix, given the current
number of internal dof. It first checks to see if the Subdomain has
changed, by  invoking {\em hasDomainChanged()} on the Subdomain; if it
has {\em invokeChangeOnAnalysis()} is invoked on the {\em
Subdomain}. It then checks to see if {\em counter} is equal to $-1$ or
not; a $-1$ indicating the tangent has already been formed in order
that the residual could be determined. If this is not the case {\em
formTangent()} is invoked on {\em theIntegrator}, {\em condenseA()} is
invoked on {\em theSolver} object, a flag is set to indicate that the
tangent has been formed, and the {\em counter} is incremented. Returns
a $0$ if successful, if either the {\em formTangent()} or {\em
condenseA()} method returns a negative number this number is
returned. \\  

{\em     virtual int  formResidual(void);}\\
A method to form the condensed residual vector, given the current
number of internal dof. A check to see if the Subdomain has changed is first made, 
this is done by invoking {\em hasDomainChanged()} on the Subdomain; if it has 
been modified {\em invokeChangeOnAnalysis()} 
is invoked on the {\em Subdomain}. If the tangent has not yet been formed
it invokes {\em formTangent()} on itself and sets the {\em counter} to $-1$.
To form the residual {\em formUnbalance()} is invoked on {\em theIntegrator} and
{\em condenseRHS(numInt)} is invoked on {\em theSolver}. Returns $0$ or the negative
number that was returned if either {\em formUnbalance()} or {\em condenseRHS()} failed.\\

{\em int  formTangVectProduct(Vector \&u);}\\
A method to form the product of the condensed tangent matrix times the
vector $u$. A check to see if the Subdomain has changed is first made, 
this is done by invoking {\em hasDomainChanged()} on the Subdomain; if it has 
been modified {\em invokeChangeOnAnalysis()} 
is invoked on the {\em Subdomain}. If the tangent has not yet been formed
it invokes {\em formTangent()} on itself and sets the {\em counter} to $-1$.
Finally the result of invoking {\em computeCondensedMatVect(numInt, u)} on {\em
theSolver} is returned. \\


{\em virtual Matrix \&getTangent();}\\
A method which returns the portion of A corresponding to internal
equation numbers. A check to see if the Subdomain has changed is first made, 
this is done by invoking {\em hasDomainChanged()} on the Subdomain; if it has 
been modified {\em invokeChangeOnAnalysis()} is invoked on the {\em Subdomain}. 
If the tangent has not yet been formed {\em formTangent()} is invoked. 
The method returns the result of invoking {\em getCondensedA()} on {\em theSolver()}. \\


{\em virtual Vector \&getResidual();}\\
A method which returns the portion of the $b$ corresponding
to the external equation numbers. A check to see if the Subdomain has changed is first made, 
this is done by invoking {\em hasDomainChanged()} on the Subdomain; if it has 
been modified {\em invokeChangeOnAnalysis()} is invoked on the {\em Subdomain}
and {\em formResidual()} is called.  The object returns the Vector obtained from 
invoking {\em getCondensedRHS()} on the solver. \\ 


{\em const Vector \&getTangVectProduct();}\\
Returns the result of invoking {\em getCondensedMatVect()} on the
solver. A check to see if the Subdomain has changed is first made, 
this is done by invoking {\em hasDomainChanged()} on the Subdomain; if it has 
been modified {\em invokeChangeOnAnalysis()} is invoked on the {\em Subdomain}. 
The object returns the Vector obtained from invoking {\em getCondensedMatVect()} 
on {\em theSolver}. \\


{\em int sendSelf(Channel \&theChannel, FEM\_ObjectBroker \&theBroker);}\\
Creates an ID and populates the ID with the class tags of the aggregates in
the aggregation. This ID is sent and then {\em sendSelf(theChannel,theBroker)} is
invoked on each of the aggregates. Returns 0.\\

{\em int recvSelf(Channel \&theChannel, FEM\_ObjectBroker \&theBroker);}\\
Creates an ID and receives data into it from {\em theChannel}. Based on the
class tags in the ID {\em theBroker} is then asked to return pointers to
new objects required in the aggregation.  {\em sendSelf(theChannel,theBroker)} is
invoked on each of these new aggregate objects. Finally {\em setLinks} is
invoked on each of these objects with the correct arguments and {\em setAnalysis(this)} 
is invoked on the {\em Subdomain}.  Returns 0.\\


\noindent {\bf Protected Methods}  \\
\indent {\em Subdomain  *getSubdomainPtr(void) const;} \\
A const member function which returns a pointer to {\em theSubdomain}. \\

{\em ConstraintHandler *getConstraintHandlerPtr(void) const;}\\
A const member function which returns a pointer to {\em theSubdomain}.\\

{\em DOF\_Numberer *getDOF\_NumbererPtr(void) const;}\\
A const member function which returns a pointer to {\em
theNumberer}.\\

{\em AnalysisModel  *getAnalysisModelPtr(void) const;}\\
A const member function which returns a pointer to {\em
theModel}.\\

{\em DomainDecompAlgo  *getDomainDecompAlgoPtr(void) const;}\\
A const member function which returns a pointer to {\em
theAlgorithm}.\\

{\em IncrementalIntegrator *getIncrementalIntegratorPtr(void) const;}\\
A const member function which returns a pointer to {\em
theIntegrator}.\\

{\em LinearSOE *getLinSOEPtr(void) const;}\\
A const member function which returns a pointer to {\em theSOE}.\\

\indent {\em DomainSolver *getDomainSolverPtr(void) const;} \\
A const member function which returns a pointer to {\em theSolver}.
associated with the DomainDecompositionAnalysis object. \\

