% File: ~/tagged/storage/TaggedObjectStorage.tex 
% What: "@(#) TaggedObjectStorage.tex, revA"

\noindent {\bf Files}   \\
\indent \#include $<\tilde{ }$/tagged/storage/TaggedObjectStorage.h$>$ \\

\noindent {\bf Class Declaration}  \\
\indent class TaggedObjectStorage  \\

\noindent {\bf Class Hierarchy} \\
\indent  {\bf TaggedObjectStorage} \\

\noindent {\bf Description}  \\
\indent TaggedObjectStorage is used as a container object to store and
provide access to objects of type TaggedObject. Each TaggedObject
object stored in a TaggedObjectStorage object must have a unique
integer tag to distinguish it from other the other objects stored. The
TaggedObjectStorage class is an abstract base class, it just defines
the interface all concrete subclasses must provide. The interface
defines methods to add and to remove the components, and methods to
obtain access to the components. \\

\noindent {\bf Class Interface}  \\
\indent // Constructor  \\
\indent {\em TaggedObjectStorage();} \\\\
\indent // Destructor \\
\indent {\em virtual  ~TaggedObjectStorage();} \\  \\
\indent // Pure Virtual Public Methods \\
\indent {\em virtual int  setSize(int newSize) =0;}\\
\indent {\em virtual bool addComponent(TaggedObject *newComponent)=0;}\\
\indent {\em virtual TaggedObject *removeComponent(int tag) =0;}\\
\indent {\em virtual int getNumComponents(void) const =0;}\\
\indent {\em virtual TaggedObject *getComponentPtr(int tag) =0;}\\
\indent {\em virtual TaggedObjectIter \&getComponents(void) =0;}\\
\indent {\em virtual TaggedObjectStorage *getEmptyCopy(void) =0;}\\
\indent {\em virtual void clearAll(bool invokeDestructor = true) =0;}\\
\indent {\em virtual void Print(ostream \&s, int flag =0) =0;}\\

\noindent {\bf Constructor} \\
\indent {\em TaggedObjectStorage();} \\
Does nothing.\\

\noindent {\bf Destructor} \\
\indent {\em virtual ~TaggedObjectStorage();} \\ 
Does nothing. Provided so that the concrete subclasses destructor will
be invoked. The subclasses destructor is NOT to delete the objects
stored in the object. {\em clearAll()} can be invoked by the
programmer if this is required. \\

\noindent {\bf Public Member Functions} \\
\indent {\em virtual int setSize(int newSize) =0;}\\
To provide an indication to the container object that {\em newSize}
components are likely to be added. This is only a hint, it should be
acceptable for more or less objects than {\em newSize} to be added to
the container. \\

\indent {\em virtual bool addComponent(TaggedObject *newComponent);}\\
To add the object {\em newComponent} to the container. To return
{\em true} if the object was added to the container, {\em false}
otherwise. The object should not be added if another object with a
similar tag already exists in the container.\\
 
\indent {\em virtual TaggedObject *removeComponent(int tag) =0;}\\
To remove the component whose tag is given by {\em tag} from the
container. To return a pointer to the removed object if successful,
$0$ if not.\\ 

\indent {\em virtual int  getNumComponents(void) const =0;}\\
To return the number of components currently stored in the container. \\

\indent {\em virtual TaggedObject *getComponentPtr(int tag) =0;}\\
To return a pointer to the TaggedObject whose identifier is given by
{\em tag}. If the object has not been added to the container $0$ is to
be returned. \\

\indent {\em virtual TaggedObjectIter \&getComponents(void) =0;}\\
To return an iter for iterating through the objects that have been
added to the container. \\

\indent {\em virtual TaggedObjectStorage *getEmptyCopy(void) =0;}\\
To return an empty copy of the container. \\

\indent {\em virtual void clearAll(bool invokeDestructor = true) =0;}\\
To remove all objects from the container and {\bf to invoke the
destructor on these objects} if {\em invokeDestructor} is {\em true}. \\

\indent {\em virtual void Print(ostream \&s, int flag =0) =0;}\\
To invoke {\em Print(s,flag)} on all objects which have been added to
the container. 





