\noindent {\bf Files}   \\
\indent \#include $<\tilde{ }$/material/nD/BidirectionalMaterial.h$>$  \\

\noindent {\bf Class Declaration}  \\
\indent class BidirectionalMaterial : public NDMaterial \\

\noindent {\bf Class Hierarchy} \\
\indent TaggedObject \\
\indent MovableObject \\
\indent\indent Material \\
\indent\indent\indent NDMaterial \\
\indent\indent\indent\indent {\bf BidirectionalMaterial} \\

\noindent {\bf Description}  \\
\indent BidirectionalMaterial is an implementation of NDMaterial. 
BidirectionalMaterial is a two-dimensional elasto-plastic material model with
combined linear isotropic and kinematic hardening. The yield surface is
circular with a specified radius. A radial return map algorithm is used
in the state determination. \\

\noindent {\bf Class Interface} \\
\indent // Constructors \\
\indent {\em BidirectionalMaterial(int tag, double E, double fy, double Hiso, double Hkin);} \\ 
\indent {\em BidirectionalMaterial();} \\ \\
\indent // Destructor \\
\indent {\em $\tilde{ }$BidirectionalMaterial();} \\ \\
\indent // Public Methods \\
\indent {\em int setTrialStrain(const Vector \&strain); } \\
\indent {\em const Vector \&getStrain(void); } \\
\indent {\em const Vector \&getStress(void); } \\
\indent {\em const Matrix \&getTangent(void); } \\
\indent {\em int commitState(void); } \\
\indent {\em int revertToLastCommit(void); } \\
\indent {\em int revertToStart(void); } \\
\indent {\em NDMaterial *getCopy(void); } \\ \\
\indent // Public Methods for Output\\
\indent {\em int sendSelf(int commitTag, Channel \&theChannel); } \\
\indent {\em int recvSelf(int commitTag, Channel \&theChannel, 
FEM\_ObjectBroker \&theBroker); } \\
\indent {\em void Print(ostream \&s, int flag = 0);} \\

\noindent {\bf Constructors} \\
\indent {\em BidirectionalMaterial(int tag, double E, double fy, double Hiso, double Hkin);} \\
Constructs a BidirectionalMaterial whose unique integer among
NDMaterials in the domain is given by {\em tag}.
Sets the elastic modulus to {\em E}, initial yield stress
to {\em fy}, and isotropic and kinematic hardening moduli to 
{\em Hiso} and {\em Hkin}, respectively. Sets all committed history
variables to $0.0$. The integers {\em tag} and ND\_TAG\_Bidirectional, 
defined in $<$classTags.h$>$, are passed to the NDMaterial 
constructor. \\ 

\indent {\em BidirectionalMaterial();} \\
Constructs a BidirectionalMaterial with tag 0. All material parameters
and committed history variables are set to $0.0$. The integers 0 and 
ND\_TAG\_Bidirectional, defined in $<$classTags.h$>$, are passed to 
the NDMaterial constructor. \\ 

\noindent {\bf Destructor} \\
\indent {\em $\tilde{ }$BidirectionalMaterial();} \\
Does nothing. \\

\noindent {\bf Public Methods} \\
\indent {\em int setTrialStrain(const Vector \&strain); } \\
Sets the trial strain of this material to be {\em strain}. Returns 0. \\

\indent {\em const Vector \&getStrain(void); } \\
Returns the current trial strain of this material. \\

\indent {\em const Vector \&getStress(void); } \\
Returns the current stress computed by the radial return mapping algorithm. This
is the 2d generalization of the 1d algorithm described in Simo \& Hughes (1998),
Box $1.5$. \\

\indent {\em const Matrix \&getTangent(void); } \\
Returns the tangent consistent with the stress computed by the radial
return mapping algorithm in {\em getStress()}. \\

\indent {\em int commitState(void); } \\
Sets the committed history variables to be their corresponding trial
values. Returns 0. \\

\indent {\em int revertToLastCommit(void); } \\
Does nothing. Returns 0. \\

\indent {\em int revertToStart(void); } \\
Sets all committed history variables to $0.0$. Returns 0. \\

\indent {\em NDMaterial *getCopy(void); } \\
Returns a pointer to a new instance of BidirectionalMaterial with the 
same tag, elastic modulus, initial yield stress, and 
hardening moduli. Copies the committed history variables to the 
new object. It is up to the caller to invoke the destructor. \\

\indent {\em int sendSelf(int commitTag, Channel \&theChannel); }\\
Returns 0 if successful and a negative number if any of the 
send operation fails. \\

\indent {\em int recvSelf(int commitTag, Channel \&theChannel, 
FEM\_ObjectBroker \&theBroker); }\\
Returns 0 if successful and a negative number if any of the 
receive operation fails. \\

\indent {\em void Print(ostream \&s, int flag);} \\
Prints the tag of this object and its elastic modulus, initial yield
stress, and hardening moduli to the stream {\em s}.
