%File: ~/OOP/analysis/analysis/StaticAnalysis.tex
%What: "@(#) StaticAnalysis.tex, revA"

\noindent {\bf Files}   \\
\indent \#include $<\tilde{ }$/analysis/analysis/StaticAnalysis.h$>$  \\

\noindent {\bf Class Declaration}  \\
\indent class StaticAnalysis: public Analysis;  \\

\noindent {\bf Class Hierarchy} \\
\indent Analysis \\
\indent\indent {\bf StaticAnalysis} \\

\noindent {\bf Description} \\ 
\indent StaticAnalysis is a subclass of Analysis, it is used to
perform a static analysis on the Domain. The following are the
aggregates of such an analysis type: 
\begin{itemize}
\item {\bf AnalysisModel} - a container class holding the FE\_Element
and DOF\_Group objects created by the ConstraintHandler object. 
\item {\bf ConstraintHandler} - a class which creates the DOF\_Group
and FE\_Element objects, the type of objects created depending on how
the specified constraints in the domain are to be handled. 
\item {\bf DOF\_Numberer} - a class responsible for providing equation
numbers to the individual degrees of freedom in each DOF\_Group object.
\item {\bf LinearSOE} - a numeric class responsible for the creation
and subsequent solution of large systems of linear equations of the
form $Ax = b$, where $A$ is a matrix and $x$ and $b$ are vectors.
\item {\bf StaticIntegrator} - an algorithmic class which provides
methods which are invoked by the FE\_Element to determine their
current tangent and residual matrices; that is this is the class that
sets up the system of equations.  It also provides the {\em
update()} method which is invoked to set up the appropriate dof
response values once the solution algorithm has formed and solved the
system of equations.
\item {\bf EquiSolnAlgo} - an algorithmic class specifying the
sequence of operations to be performed in setting up and solving the
finite element equation which can be represented by the equation K(U)
U = P(U). 
\end{itemize}

\noindent {\bf Class Interface} \\
\indent // Constructors \\
\indent {\em StaticAnalysis(Domain \&theDomain, \\
\indent\indent\indent\indent ConstraintHandler \&theHandler, \\
\indent\indent\indent\indent DOF\_Numberer \&theNumberer, \\
\indent\indent\indent\indent AnalysisModel \&theModel,\\
\indent\indent\indent\indent EquiSolnAlgo \&theSolnAlgo,\\
\indent\indent\indent\indent LinearSOE \&theSOE, \\
\indent\indent\indent\indent StaticIntegrator \&theIntegrator \\
\indent\indent\indent\indent int numIncrements = 1);} \\ \\
\indent // Destructor \\
\indent {\em virtual~ $\tilde{}$StaticAnalysis();}\\  \\
\indent // Public Methods\\
\indent {\em int analyze(void);} \\
\indent {\em void clearAll(void);} \\
\indent {\em int domainChange(void);}\\  \\
\indent // Public Methods to vary the type of Analysis\\
\indent {\em int setNumIncrements(int numIncrements);}\\ 
\indent {\em int setAlgorithm(EquiSolnAlgo \&theAlgorithm);} \\
\indent {\em int setIntegrator(StaticIntegrator \&theIntegrator);}\\
\indent {\em int setLinearSOE(LinearSOE \&theSOE);} \\

\noindent {\bf Constructors} \\
\indent {\em StaticAnalysis(Domain \&theDomain, \\
\indent\indent\indent\indent\indent ConstraintHandler \&theHandler, \\
\indent\indent\indent\indent\indent DOF\_Numberer \&theNumberer, \\
\indent\indent\indent\indent\indent AnalysisModel \&theModel,\\
\indent\indent\indent\indent\indent EquiSolnAlgo \&theSolnAlgo,\\
\indent\indent\indent\indent\indent LinearSOE \&theSOE, \\
\indent\indent\indent\indent\indent StaticIntegrator \&theIntegrator, \\
\indent\indent\indent\indent\indent int numIncrements = 1);} \\ \\
The constructor is responsible for setting the links between the
objects in the aggregation. To do this it invokes {\em
setLinks(theDomain)} on {\em theModel}, {\em
setLinks(theDomain,theModel,theIntegrator)} on {\em theHandler}, 
{\em setLinks(theModel)} on {\em theNumberer}, {\em
setLinks(theModel, theSOE)} on {\em theIntegrator}, and  {\em
setLinks(theModel,theAnalysis, theIntegrator, theSOE)} on {\em
theSolnAlgo}.  The constructor also sets the number of analysis steps
that will be performed to be {\em numIncrements}.\\


\noindent {\bf Destructor} \\
\indent {\em $\tilde{ }$StaticAnalysis();}\\ 
Does nothing. {\em clearAll()} must be invoked if the destructor on
the objects in the aggregation need to be invoked. \\

\noindent {\bf Public Member Functions}\\
\indent {\em int analyze(void);} \\
Invoked to perform a static analysis on the FE\_Model. The analysis 
The StaticAnalysis object performs the following:
\begin{tabbing}
while \= \+ while \= while \= \kill
    for (int i=0; i$<$ numIncrements; i++) \{ \+ \\
    if (theDomain-$>$hasDomainChanged() == true) \+\\
	this-$>$domainChanged(); \- \\
    theIntegrator.newStep(); \\
    theSolnAlgo.solveCurrentStep(); \\
    theIntegrator.commit(); \- \\ \} \\
\end{tabbing}
\noindent The type of analysis performed, depends on the type of the
objects in the analysis aggregation. If any of the methods invoked
returns a negative number, an error message is printed, {\em
revertToLastCommit()} is invoked on the Domain, and a negative number
is immediately returned. Returns a $0$ if the algorithm is successful. \\

{\em void clearAll(void);} \\
Will invoke the destructor on all the objects in the aggregation. NOTE
this means they must have been constructed using {\em new()},
otherwise a segmentation fault can occur.\\

{\em void domainChange(void);}\\
This is a method invoked by the analysis during the analysis method if
the Domain has changed. The method invokes the following:
\begin{enumerate} 
\item It invokes {\em clearAll()} on {\em theModel} which causes the
AnalysisModel to clear out its list of FE\_Elements and DOF\_Groups,
and {\em clearAll()} on {\em theHandler}.
\item It then invokes {\em handle()} on {\em theHandler}. This causes
the constraint handler to recreate the appropriate FE\_Element and
DOF\_Groups to perform the analysis subject to the boundary conditions
in the modified domain.
\item It then invokes {\em number()} on {\em theNumberer}. This causes
the DOF numberer to assign equation numbers to the individual
dof's. Once the equation numbers have been set the numberer then
invokes {\em setID()} on all the FE\_Elements in the model. Finally
the numberer invokes {\em setNumEqn()} on the model.
\item It invokes {\em setSize(theModel.getDOFGraph())} on {\em
theSOE} which causes the system of equation to determine its size
based on the connectivity of the dofs in the analysis model. 
\item Finally {\em domainChanged()} is invoked on both {\em theIntegrator} and 
{\em theAlgorithm}. 
Returns $0$ if successful. At any stage above, if an error occurs the
method is stopped, a warning message is printed and a negative number
is returned. \\ 
\end{enumerate}

\indent {\em int setNumIncrements(int numIncrements);}\\ 
To set the number of incremental steps in the analysis to be {\em
numIncrements}. Returns $0$.\\

\indent {\em int setAlgorithm(EquiSolnAlgo \&newAlgorithm);}\\
To change the algorithm between analysis. It first invokes the
destructor on the old SolutionAlgorithm object associated with the
analysis. It then sets the SolutionAlgorithm 
associated with the analysis to be {\em newAlgorithm} and sets the
links for this object by invoking {\em setLinks()}. Checks then to
see if the domain has changed, if true it invokes {\em
domainChanged()}, otherwise it invokes {\em domainChanged()} on the
new SolutionAlgorithm. Returns $0$ if successful, a warning message
and a negative number if not.\\

\indent {\em int setIntegrator(StaticIntegrator \&newIntegrator);}\\
To change the integration scheme between analysis. It first invokes the
destructor on the old Integrator object associated with the
analysis. It then sets the SolutionAlgorithm 
associated with the analysis to be {\em newAlgorithm} and sets the
links for this object by invoking {\em setLinks()}. It also invokes
{\em setLinks()} on the ConstraintHandler and SolutionAlgorithm
objects. Checks then to see if the domain has changed, if true it
invokes {\em domainChanged()}, otherwise it invokes {\em
domainChanged()} on the new Integrator. Returns $0$ if
successful, a warning message and a negative number if not.\\

\indent {\em int setLinearSOE(LinearSOE \&newSOE);}\\
To change the linear system of equation object between analysis. It
first invokes the destructor on the old LinearSOE object associated
with the analysis. It then sets the SolutionAlgorithm 
associated with the analysis to be {\em newSOE}.
links for this object by invoking {\em setLinks()}. It then invokes
{\em setLinks()} on the ConstraintHandler and SolutionAlgorithm
objects. Checks then to see if the domain has changed, if true it
invokes {\em domainChanged()}, otherwise it invokes {\em
setSize()} on the new LinearSOE. Returns $0$ if successful, a warning
message and a negative number if not.\\ 


