%File: ~/OOP/renderer/Renderer.tex
%What: "@(#) Renderer.tex, revA"

UNDER CONSTRUCTION .. POLYGONS and COLORMAP NEED A RETHINK.

\noindent {\bf Files}   \\
\indent \#include $<\tilde{ }$/earthquake/Renderer.h$>$  \\

\noindent {\bf Class Declaration}  \\
\indent class Renderer   \\

\noindent {\bf Class Hierarchy} \\
\indent {\bf Renderer} \\

\noindent {\bf Description} \\ 
\indent 
The Renderer class is an abstract class which is introduced to allow
the graphical display of the 3d finite element model. The Renderer class
is an abstract class, it defines the interface all concrete subclasses
must provide. In common with most rendering packages, the interface
allows only for the displaying of a few basic primitive objects, lines
and polygons (commercial renderers offer others such as cubes,
circles, cones). By providing only a few basic primitives, the
interface will allow complicated scenes to be created (much like the
ten digits 0-9 allows an infinite number of numbers to be created).

Unlike commercial renderers there is no concept of the optical
properties of materials and light sources in the interface. This is
because the image the analyst is looking for is not a photo realistic
image of the model, rather an image indicating the basic model,
stresses, and nodal displacements.   \\

\noindent {\bf Class Interface} \\
\indent // Constructor \\ 
\indent {\em Renderer(ColorMap \&theMap);}\\ \\
\indent // Destructor \\ 
\indent {\em virtual $\tilde{ }$Renderer();}\\  \\
\indent // Public Methods to display the Model\\ 
\indent // Public Methods invoked at start or end of a rendering\\ 
\indent {\em virtual int clearImage(void) =0;}\\
\indent {\em virtual int startImage(void) =0;}\\
\indent {\em virtual int doneImage(void) =0;}\\ \\
\indent // Public Methods invoked by the Objects to Display Themselves\\
\indent {\em virtual int drawLine(const Vector \&, const Vector \&, 
float V1, float V2) =0;}\\
\indent {\em virtual int drawLine(const Vector \&, const Vector \&, 
donst Vector \&rgb1, const Vector \&rgb2) =0;}\\
\indent {\em virtual int drawPolygon(const Vector *, const Vector \&);} \\
\indent {\em virtual int drawVector(const Vector \&position, 
const Vector \&value);}\\
\indent {\em virtual int drawGText(const Vector \&posGlobal, 
char *string, int length);}\\
\indent {\em virtual int drawLText(const Vector \&posLocal, 
char *string, int length); }\\
\indent {\em void setColorMap(ColorMap \&theMap);}\\ \\
\indent // Public Methods invoked to set up the viewing system \\
\indent {\em virtual int setVRP(float x, float y, float z) =0;}\\
\indent {\em virtual int setVPN(float x, float y, float z) =0;}\\
\indent {\em virtual int setVUP(float x, float y, float z) =0;}\\
\indent {\em virtual int setViewWindow(float uMin, float uMax, float
vMin, float vMax) =0;}\\
\indent {\em    virtual int setPlaneDist(float nearPlane, float farPlane) =0;}\\
\indent {\em    virtual int setProjectionMode(int) =0;}\\ 
\indent {\em    virtual int setFillMode(int) =0;}\\
\indent {\em    virtual int setPRP(float u, float v, float n) =0;}\\
\indent {\em    virtual int setPortWindow(float, float, float, float) =0;}\\


\noindent {\bf Constructor} \\ 
\indent {\em Renderer(Domain \&theDomain, ColorMap \&theMap);}\\ 
Keeps a pointer to Domain object {\em theDomain} and the ColorMap
object {\em theMap}. \\

\noindent {\bf Destructor} \\
\indent {\em virtual $\tilde{ }$Renderer();}\\  
Does Noting. \\

\noindent {\bf Public Methods} \\
\indent {\em virtual int clearImage(void) =0;}\\
Invoked to clear the image. This is required if multiple images can be
displayed at once for example in a graphic window. \\

\indent {\em virtual int startImage(void) =0;}\\
Invoked at the start of {\em displayModel()}, when the image is about
to be displayed. \\

\indent {\em virtual int doneImage(void) =0;}\\
Invoked at the end of {\em displayModel()}, when the image is finished
and ready to be displayed. \\

\indent {\em virtual int drawLine(const Vector \&end1, const Vector \&end2, 
float V1, float V2) =0;}\\
Invoked to draw a line in the image. The two vectors {\em end1} and
{\em end2} define the two end points in the 3d coordinate system, the
values {\em V1} and {\em V2} define the scalar quantity to be
displayed. To return $0$ if successful, a negative number if not.\\



\indent {\em virtual int drawPolygon(const Vector *ends, const Vector
\&values);} \\ 
Invoked to draw a polygon in the image. The Vectors pointed to in {\em
ends} define the end points of the polygon and the Vector {\em values}
define the scalar quantities to be displayed. Note that there must
be at least {\em values.Size()} Vectors pointed to at the start of
{\em ends}, otherwise a segmentation fault will occur. To return $0$
if successful, a negative number if not.\\

\indent {\em virtual int drawVector(const Vector \&position, 
const Vector \&value);}\\
Invoked to draw a vector in the image. The vector is to be drawn
at position {\em position}. The magnitude and direction of the vector
are given in {\em value}. To return $0$ if successful, a negative
number if not.\\ 


\indent {\em virtual int drawGText(const Vector \&posGlobal, 
char *string, int length);}\\
Invoked to draw a string of text in the image at position {\em
posGlobal}. The position is in the 3d model coordinates. The length of
the string is {\em length}. To return $0$ if successful, a negative
number if not.\\ 


\indent {\em virtual int drawLText(const Vector \&posLocal, 
char *string, int length); }\\
Invoked to draw a string of text in the image at position {\em
posGlobal}. The position is in the 3d model coordinates. The length of
the string is {\em length}. To return $0$ if successful, a negative
number if not.\\ 

\indent {\em void setColorMap(ColorMap \&theMap);}\\
To set the ColorMap used in the {\em draw()} routines. The ColorMap
object is used to convert scalar quantities into rgb values. 


\indent {\em virtual int setVRP(float x, float y, float z) =0;}\\
Invoked to set the VRP. The VRP is a point on the viewing plane, which
is that plane in the global coordinate system on which the 3d image is
projected. The point is given in the global coordinate system. \\

\indent {\em virtual int setVPN(float x, float y, float z) =0;}\\
Invoked to set the VPN. The VPN defines the perpendicular to the
viewing plane. \\

\indent {\em virtual int setVUP(float x, float y, float z) =0;}\\
Invoked to set the VUP. The VUP defines the up direction of the
viewing plane. The combination of VRP, VPN and VUP define a new local
coordinate system centered at VRP, with axis u,v,n, where the
direction of u is given by $vuv \% vpn$, v by $vpn \% u$ and n
finishes off the rhs local system. \\

\indent {\em virtual int setViewWindow(float uMin, float uMax, float
vMin, float vMax) =0;}\\
Invoked to set the bounds of the image on the view plane which is then
scaled to fit into the image displayed. The values provided are in the
local coordinate system. \\

\indent {\em virtual int setPlaneDist(float nearPlane, float farPlane)
=0;}\\
Sets the distance to the near and far clipping planes. \\

\indent {\em    virtual int setProjectionMode(int mode) =0;}\\ 
Sets the projection mode. If mode is $0$ a parallel projection of the
image onto the viewing plane will be displayed, if $1$ a perspective
projection. \\

\indent {\em    virtual int setFillMode(int mode) =0;}\\
Sets the fill mode for solid shapes, i.e. polygons. If {\em mode} is
$0$ a wire frame image will be displayed, otherwise solid shapes will
be filled. \\

\indent {\em    virtual int setPRP(float u, float v, float n) =0;}\\
Sets the PRP. The PRP defines the eye location of the viewer. It is
important to note that the eye location is specified in the new local
coordinate system. \\

\indent {\em    virtual int setPortWindow(float, float, float, float)
=0;}\\ 
Sets the portwindow. The portwindow is that region of the display
into which the image is displayed. The range is [-1,1.-1.1]. \\